\chapter{Project}
\section{General}
\begin{description}
  \item[Euler equations:] discontinuous finite elements stabilized by entropy
    viscosity.
  \item[Radiative transfer:] discontinuous finite elements, matrix-free,
    need for fixup (?), preconditioned by (adapted?) MIP.
  \item[JFNK and operator.]
  \item[((SD)I)RK methods:] use different time discretizations for different
    equations.
  \item[AMR:] one mesh per physics.
\end{description}

\section{General structure}
\begin{description}
  \item[Material properties:] properties from table and/or equations.
    Different physics require different material properties.
    \begin{table}[H]
      \centering
      \begin{tabular}{|c|c|c|c|c|c|c|}
        \hline
        Interface & \multicolumn{6}{c|}{Material Properties} \\
        \hline
        Base class & \multicolumn{2}{c|}{Fluid properties} &
      \multicolumn{2}{c|}{R.T. properties} & \multicolumn{2}{c|}{Kinetic properties}
        \\
        \hline
        Derived class & Table & Formula & Table & Formula & Table & Formula \\
        \hline
      \end{tabular}
    \end{table}
  \item[Time discretization:] different discretizations coded by Butcher
    tables.
  \item[Physics:] base class for the physics: wrapper around
    Belos::LinearProblem so that it is easy to have a matrix-free physics
    $\rightarrow$ implement Tpetra and Belos in deal.II. Used for operator
    split. The different physics are derived from this class.
  \item[Radiative transfer:] derived from physics.
  \item[Preconditioner:] base class for the preconditioners of the physics
    problems (ex. MIP).
  \item[Newton:] build the Jacobian or an approximation of the Jacobian if
    necessary and perform the Newton's iterations.
  \item[Preconditioner of the Jacobian:] preconditioner for the Jacobian.
  \item[Parameters:] contain all the parameters of the problems.
\end{description}

\section{Detailed structure}
\subsection{Radiative transfer material properties}
\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|}
    \hline
    Public methods & Private methods & Members \\
    \hline
                   &                 & $\Sigma_t$ \\
                   &                 & $\Sigma_s$ \\
    \hline
  \end{tabular}
\end{table}

